Analysis of bulk void regions

### 2014-04-20 cosmic_voids.tex
Analysis of distributions of mass and peculiar velocity of dark matter halos

The more notorious characteristic of Figure \ref{fig:halos_fractions} is
the behaviour of the fraction of halos within sheet regions for both web 
schemes, increasing until a local maximum, and then decreasing. The 
increasing or decreasing rate of the fraction of halos for some region 
could be interpreted as a measure of the degree of non-linearity of such 
region for some specific \lth value. For example, filaments and knots, 
that are the most non-linear regions of the universe, have a negative rate 
for all covered \lth range. In the case of voids, the situation is 
completely opposite, where fractions of halos increase in everywhere. If 
we think in terms of the underlying matter field of the cosmic web, \lth 
is just a cutting parameter between high non-linear regions (filament and 
knots) and low non-linear (voids and sheets). Furthermore, if we take into 
account that dark matter halos are much more likely to form in high 
non-linear regions, it is expected the obtained behaviour of fractions of 
halos for voids, filaments and knots as we increase the \lth value. 
However, the behaviour of the fraction of halos in sheets is less clear,
increasing for low \lth values (like voids) and decreasing for higher \lth 
values (like filaments and knots). This indicates us the transitional 
character of sheet regions in the cosmic web. Our proposal here is to 
select as optimal \lth the value where the fraction of sheets reaches a
local maximum, so sheets are completely taken as intermediate transitional 
and neutral zones regarding the degree of non-linearity. According to this,
we find for the T-web scheme a optimal value $\lambda_{opt}^T = 0.36$ and
for the V-web scheme $\lambda_{opt}^V = 0.20$. In figure 
\ref{fig:visual_impression} we show the visual impression of the cosmic 
web along with the density field for different \lth values including the 
optimal values.

@@

  \captionof{figure}{\small Mean density parameter for each one of the 
  defined environments according to the chosen $\lambda_{th}$ value and 
  for both classification schemes. Tweb (green lines) and Vweb (blue 
  lines). The mean density parameter is calculated by averaging all the 
  values  of the cells determined as a certain type of environment 
  according to its eigenvalues. The optimal parameters found are 
  $\lambda_{opt}^{T}=0.326$ and $\lambda_{opt}^{V}=0.188$.}

@@

  \includegraphics[trim = 42mm 15mm 37mm 10mm, clip, keepaspectratio=true,
  width=0.75\textheight]{./figures/cosmicweb_visual_Tweb.pdf}
  \includegraphics[trim = 42mm 15mm 37mm 10mm, clip, keepaspectratio=true,
  width=0.75\textheight]{./figures/cosmicweb_visual_Vweb.pdf}

@@

>>>>

The more notorious characteristic of Figure \ref{fig:halos_fractions} is
the behaviour of the fraction of halos within sheet regions for both web 
schemes, increasing until a local maximum, and then decreasing. The 
increasing or decreasing rate of the fraction of halos for some region 
could be interpreted as a measure of the degree of non-linearity of such 
region for some specific \lth value. For example, filaments and knots, 
that are the most non-linear regions of the universe, have a negative rate 
for all covered \lth range. In the case of voids, the situation is 
completely opposite, where fractions of halos increase in everywhere. If 
we think in terms of the underlying matter field of the cosmic web, \lth 
is just a cutting parameter between high non-linear regions (filament and 
knots) and low non-linear (voids and sheets). Furthermore, if we take into 
account that dark matter halos are much more likely to form in high 
non-linear regions, it is expected the obtained behaviour of fractions of 
halos for voids, filaments and knots as we increase the \lth value. 
However, the behaviour of the fraction of halos in sheets is less clear,
increasing for low \lth values (like voids) and decreasing for higher \lth 
values (like filaments and knots). This indicates us the transitional 
character of sheet regions in the cosmic web. Our proposal here is to 
select as optimal \lth the value where the fraction of sheets reaches a
local maximum, so sheets are completely taken as intermediate transitional 
and neutral zones regarding the degree of non-linearity. According to this,
we find for the T-web scheme an optimal value $\lambda_{opt}^T = 0.36$ and
for the V-web scheme $\lambda_{opt}^V = 0.20$. In figure 
\ref{fig:visual_impression} we show the visual impression of the cosmic 
web along with the density field for different \lth values including the 
optimal values. It can be noticed that the optimal values found reproduce 
well the visual impression.

As we have taken halos as tracers of the cosmic web, we analyse 
distributions of mass and peculiar velocity in order to assign typical 
values to each type of environment. In figure 
\ref{fig:typical_mass_velocity} we calculate both distributions for web 
schemes and using the FOF catalogue of the simulation. Thick lines 
correspond to the median of the distribution and filled regions limited by
dashed lines correspond to quartiles $Q_1$ and $Q_3$, it means, $50\%$ of
all halos are within such regions for every \lth value and for each type of
environment. We rather use median and quartiles as measure of dispersion 
because there are some very unusual and extreme values that makes the usual
analysis based upon means and standard deviations less reliable.

A first interesting feature of Figure  \ref{fig:typical_mass_velocity} is 
the median mass for each region. In the case of the T-web, although 
dispersions of the distribution of mass for each environment are 
considerably overlapped each other, the median value is very 
well-differentiated among types of environment, indicating that it is 
possible to assign typical values of mass to each region, and being 
consistent with expectations, where low mass halos are typical in voids 
until high mass halos in knots. For the case of the V-web scheme, all
medians and dispersions are completely overlapped, specially for values 
grater than the optimal \lth value, indicating that it is not possible to
assign typical mass ranges to each environment as quantified by this 
scheme. For peculiar velocities, this situation is opposite, where V-web
scheme is much more adequate to assign typical distributions of velocity
to each environment. Although T-web also makes a differentiation in the 
distributions of velocity, this is very slight compared with the V-web 
case. These results can be explained by appealing the physical origin of 
each web scheme. As T-web is based upon the Hessian matrix of the potential
field, it is expected all quantities related to the potential, like density
field and distribution of halos mass, are well-differentiated among each 
region, while for the V-web scheme, based upon the shear velocity tensor, 
all dynamical quantities, as the peculiar velocity field and the 
distribution of halos velocity are alike expected to be 
well-differentiated among regions as quantified by this scheme.

Finally, we also calculate typical distributions of the density and 
peculiar velocity fields in each type of environment, obtaining completely 
analogous results. Furthermore, we also use a BDM catalogue of the 
simulation, obtaining very similar conclusions.

@@

  \captionof{figure}{\small Fractions of halos embedded in each one of 
  the defined environments according to the \lth value. T-web scheme 
  (upper panel) and V-web scheme (lower panel). The optimal parameters 
  found are $\lambda_{opt}^{T}=0.36$ and $\lambda_{opt}^{V}=0.20$.}

@@

  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
  width=0.75\textheight]{./figures/cosmicweb_visual_Tweb.pdf}
  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
  width=0.75\textheight]{./figures/cosmicweb_visual_Vweb.pdf}

@@

%.........................................................................
%FIGURE 3: Typical mass and pecular velocity
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/halos_typical_mass_FOF_Tweb.pdf}
  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/halos_typical_mass_FOF_Vweb.pdf}

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/halos_typical_velocity_FOF_Tweb.pdf}
  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/halos_typical_velocity_FOF_Vweb.pdf}

  \captionof{figure}{\small Distribution of masses of dark matter halos
  according the region where they are embedded for both web schemes 
  (upper panels) and of peculiar velocity (lower| panels).}

  \label{fig:typical_mass_velocity}
  \vspace{0.1 cm}
